---
title: Assessing replication rates in journals of experimental linguistics
author:
  - name: Kristina Kobrock
    email: kkobrock@uni-osnabrueck.de
    affiliation: University of Osnabrück
    footnote: 1
  - name: Timo B. Roettger
    #email: bob@example.com
    affiliation: University of Oslo
address:
  - code: University of Osnabrück
    address: Department, Street, City, State, Zip
  - code: University of Oslo
    address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  This is the abstract.

  It consists of two paragraphs.

journal: "Journal of Memory and Language"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---
# Introduction
state the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results

# Material and methods
provide sufficient details to allow the work to be reproduced by an independent researcher, describe any modifications to existing methods

# Results
clear and concise, include tables and figures
```{r message=FALSE, warning=FALSE, echo=FALSE}
## load in library
library(tidyverse)
library(truncnorm)
library(brms)
library(rstudioapi)
library(ggdist)
library(distributional)
library(ggstream)

## package for visualization
library(tidybayes)
library(bayesplot)
```
```{r echo=FALSE}
## global color scheme / non-optimized
### purple
col_purple = "#7b3294"
### light purple
col_lightPurple = "#c2a5cf"
### green
col_green = "#008837"
### light green
col_lightGreen = "#a6dba0"
```

```{r loading data, echo=FALSE}
# loading the data
coded_articles = read.csv("../../data/Coding_Articles.csv", sep="|")
nr_replications = coded_articles %>% filter(replication == "1") %>% count() # 117 are replications
```
```{r success, echo=FALSE}
# How many of the direct replications were (self-labeled) successful?
direct_reps = coded_articles %>% filter(type_replication == "direct") %>% count() # 8 direct replications
success_reps = coded_articles %>% filter(type_replication == "direct") %>% filter(success == "1") %>% count() # 7 successful
success_rate = (success_reps / direct_reps) * 100
# --> 87,5%
```
```{r years between, echo=FALSE}
# What is the mean and median number of years between an initial and a replication study?
coded_articles %>% 
  filter(cit_init_study != "same") %>% # exclude inner-paper replications
  summarise(mean_years = mean(years_between, na.rm = TRUE)) # ~ 8,81 years
coded_articles %>% 
  filter(cit_init_study != "same") %>% # exclude inner-paper replications
  summarise(median_years = median(years_between, na.rm = TRUE)) # 7 years
```
```{r citation, echo=FALSE}
# What is the mean and median citation count of initial studies before a replication study was published?
coded_articles %>% 
  filter(cit_init_study != "same") %>% # exclude inner-paper replications
  summarise(mean_cit_init = mean(init_cit_til_rep, na.rm = TRUE)) # ~ 41,1 citations
coded_articles %>% 
  filter(cit_init_study != "same") %>% # exclude inner-paper replications
  summarise(median_cit_init = median(init_cit_til_rep, na.rm = TRUE)) # 19,5 citations
```
```{r plot cit and years direct, echo=FALSE, message=FALSE}
# preparing data for plot

# wrangling citation data
cit_data <- coded_articles %>% 
  filter(type_replication == "direct") %>% # only include direct replications
  mutate(
    obs_nr = c(1:8)
  ) %>% 
  select(obs_nr, rep_citation, init_cit_til_rep) %>% 
  pivot_longer(cols = c(rep_citation, init_cit_til_rep), values_to = "citation") %>% 
  mutate(
    study_kind = ifelse(name == "rep_citation", "replication", "initial")
  ) %>% 
  select(obs_nr, study_kind, citation)

# wrangling year of publication data
pub_data <- coded_articles %>% 
  filter(type_replication == "direct") %>% # only include direct replications
  mutate(
    obs_nr = c(1:8)
  ) %>%
  select(obs_nr, pub_year, year_init_study) %>% 
  pivot_longer(cols = c(pub_year, year_init_study), values_to = "years") %>% 
  mutate(
    study_kind = ifelse(name == "pub_year", "replication", "initial")
  ) %>% 
  select(obs_nr, study_kind, years)

# creating one data frame for plotting
plot_data <- full_join(cit_data, pub_data)

# creating a plot
plot_data %>% 
  ggplot(aes(x = years, y = citation, color = study_kind, group = obs_nr)) +
  geom_point() +
  geom_line(color = "lightgrey") +
  labs(
    x = "years",
    y = "citations",
    title = "After how many years and how many citations do replication studies get published?"
  )
```
```{r plot cit and years all, echo=FALSE, message=FALSE, warning=FALSE}
# preparing data for plot

# wrangling citation data
cit_data <- coded_articles %>% 
  filter(replication == "1") %>% # only include replications
  mutate(
    obs_nr = c(1:117)
  ) %>% 
  select(obs_nr, rep_citation, init_cit_til_rep) %>% 
  pivot_longer(cols = c(rep_citation, init_cit_til_rep), values_to = "citation") %>% 
  mutate(
    study_kind = ifelse(name == "rep_citation", "replication", "initial")
  ) %>% 
  select(obs_nr, study_kind, citation)

# wrangling year of publication data
pub_data <- coded_articles %>% 
  filter(replication == "1") %>% # only include replications
  mutate(
    obs_nr = c(1:117)
  ) %>%
  select(obs_nr, pub_year, year_init_study) %>% 
  pivot_longer(cols = c(pub_year, year_init_study), values_to = "years") %>% 
  mutate(
    study_kind = ifelse(name == "pub_year", "replication", "initial")
  ) %>% 
  select(obs_nr, study_kind, years)

# creating one data frame for plotting
plot_data <- full_join(cit_data, pub_data)

# creating a plot
plot_data %>% 
  ggplot(aes(x = years, y = citation, color = study_kind, group = obs_nr)) +
  geom_point() +
  geom_line(color = "lightgrey") +
  labs(
    x = "years",
    y = "citations",
    title = "After how many years and how many citations do replication studies get published?"
  )
```
```{r inner paper, echo=FALSE}
# How many replication studies were inner-paper replications?
reps_inner_paper = coded_articles %>% 
  filter(replication == "1") %>% 
  filter(cit_init_study == "same") %>% 
  count() 
# --> 37
inner_paper = (reps_inner_paper / nr_replications) * 100
# --> ~ 31,62 %
```
```{r language rep, echo=FALSE}
# How many replication studies were replications in a different language?
reps_diff_lang = coded_articles %>% 
  filter(replication == "1") %>% 
  filter(str_detect(comments, "replication in a different language")) %>% 
  count()
# --> 18
diff_lang = (reps_diff_lang / nr_replications) * 100
# --> ~ 15,38 %
```
```{r same journal, echo=FALSE}
# How many replication studies were published in the same journal?
journal_init = factor(coded_articles$journal_init_study, levels = levels(coded_articles$journal)) # set levels equal
reps_same_journal = coded_articles %>% 
  filter(journal == journal_init) %>% 
  filter(cit_init_study != "same") %>% # exclude inner-paper studies
  count()
# --> 16 (52 without exclusion)
same_journal = (reps_same_journal / nr_replications) * 100
# --> ~ 13,68 %
```
```{r jml}
# having a closer look at jml
jml_data <- coded_articles %>% 
  filter(journal == "JOURNAL OF MEMORY AND LANGUAGE")

## how many really experimental
jml_exp <- jml_data %>% 
  filter(experimental == "1") 
jml_exp_ratio = count(jml_exp)/count(jml_data) 
# ---> 50 = 100%

## of those how many actual replications
jml_reps <- jml_exp %>% 
  filter(replication == "1")
jml_rep_ratio = count(jml_reps)/count(jml_exp)
# ---> 34 = 68%

## of those what types of replications
round(xtabs(~type_replication, jml_reps) / nrow(jml_reps), 2)
### 0.44 conceptual
### 0.09 direct --> compared to 7% over all journals
### 0.47 partial

## of those author overlap
round(xtabs(~type_replication + auth_overlap, jml_reps) / nrow(jml_reps), 2)
###            no   yes 
### conceptual 0.18 0.26
### direct     0.06 0.03
### partial    0.24 0.24

# all journals:
###            no   yes 
### conceptual 0.26 0.30
### direct     0.03 0.04
### partial    0.15 0.21

## overall direct independent replication rate 
round(nrow(jml_data[jml_data$replication == 1 &
                jml_data$type_replication == "direct" &
                jml_data$auth_overlap == 0,]) / nrow(jml_data), 3)
### 0.04 = 4% compared to 0.015 = 1,5%
```

# Discussion

# Appendices
identified as A, B, etc.

Bibliography styles
===================

There are various bibliography styles available. You can select the
style of your choice in the preamble of this document. These styles are
Elsevier styles based on standard styles like Harvard and Vancouver.
Please use BibTeX to generate your bibliography and include DOIs
whenever available.

Here are two sample references: @Feynman1963118 [@Dirac1953888].

References {#references .unnumbered}
==========
